A secure and trustworthy internet needs computationally intensive cryptography
algorithms. For security, performance and applicability to multiple platforms,
it is best if these algorithms are executed in hardware with some of the
flexibility of software.

The OpenCryptoHW project, funded by the NGI Assure program, proposed the use of
Coarse Grained Reconfigurable Arrays (CGRAs)~\cite{bla} to accomplish this
objective, and chose the SHA256 and the AES256 algorithms to illustrate the
ideas proposed.

The project's assumptions are the following: internet devices use a main Central
Processing Unit and an Ethernet Medium Access Controller (MAC) core. Each
internet device is engaged in frequent secure network communications. To ensure
trust, the software and hardware descriptions must be open-source. OpenCryptoHW
uses the VexRiscV processor~\cite{} and the IOb-Eth MAC core~\cite{iob-eth} to
accomplish these objectives. Moreover, it uses the IOb-Versat
CGRA~\cite{iob-versat} to accelerate the cryptography algorithms.

This document describes the SHA256~\cite{SHA_NIST_FIPS} acceleration plan
running on the IOb-SoC-SHA system~\cite{iob-soc-sha}, according to Milestone 7 of
the OpenCryptoHW project. The document is divided in four parts:
\begin{itemize}
\item the first part provides a brief introduction to the SHA-256 algorithm.
\item the second part presents profiling data for the SHA256 application
    running exclusively on the riscv CPU.
\item the third part elaborates on the profiling conclusions and establishes
    functional unit architectures to accelerate the application.
\item the fourth part outlines a prediction for the expected resutls from
    implementing the acceleration strategy.
\end{itemize}










